\documentclass{beamer}
\usetheme{CambridgeUS}
\begin{document}
\newcommand{\bfr}[2]{\section{#1} \begin{frame}{#1} #2 \end{frame}}

\title{Project 2 : EMS in the world}
		\author{ Archit Vivek Ganvir}

	\begin{frame}
    		\titlepage 
	\end{frame}
	
	\begin{frame}
		\tableofcontents
	\end{frame}

\bfr{What is an EMS?}{

An EMS, or Education Management System, is a framework of people and machines that aim to streamline the process of education, primarily by optimizing accessibility and quality of content for students.

\begin{itemize}
    \item Some of the most popular Education Management Systems used in India are Byju's and Unacademy, and their working will be familiar to most students. 

    \item They offer vast amounts of comprehensive study material across all stages of education, from primary school to competitive national exams and olympiads.

    \item These also track the students' progress through various courses and tests, and provide a detailed analysis for the students to evaluate their strengths and weaknesses. These statistics are well represented so as to build an intuition of what progress looks like in students, using graphs, pie-charts, and various other pictorial means.

\end{itemize}

}

\bfr{Some Education Management Systems}{

\begin{itemize}

\item Byju's also provides interactive videos and tests, which has helped it reach the position of the best Education Management System in India.

\item Unacademy offers a variety of online courses, which the students can complete at their own pace, and, at the same time, have their doubts cleared by teachers.

\item As far as innovations go, Doubtnut offers a very useful feature : students can directly scan their question from a camera or an image, and the software automatically finds a solution from the millions of solutions available in their database. It has a very interactive website and mobile app; moreover, it also has a WhatsApp bot that lets students directly upload a photo of a question, and then provides links to solutions.

\item Perhaps the best one out there, Khanacademy is an Education Management System that has received widespread acclaim internationally, and provides structured and lucid recordings that ensure concept clarity. The advent of Khanacademy is widely believed to have revolutionized education in several countries.

\item All Education Management Systems are built around the core intent of optimized dissemination of educational information, and each iteration has offered its own innovations that attempt to enhance connectivity and hence achieve conceptual clarity.

\end{itemize}

}

\bfr{What an EMS does}{

\begin{itemize}

\item To summarise, these popular EMIS's provide the ability to download lots of online resources such as textbooks, solutions, notes, solved question papers, reference books, video lectures, etc..

\item They also provide students with a detailed analysis of their progress through various courses and tests.

\item They also provide a platform/forum where students and teachers can discuss about any topic.

\end{itemize}

}

\end{document}