%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% Inbuilt themes in beamer
\documentclass{beamer}

% Theme choice:
\usetheme{CambridgeUS}

% Title page details: 
\usepackage[parfill]{parskip}

\pagecolor{white}
\DeclareMathOperator*{\Res}{Res}
\DeclareMathOperator*{\equals}{=}
\DeclareMathOperator*{\pipe}{|}

\hyphenation{op-tical net-works semi-conduc-tor}
\def\inputGnumericTable{}  
\graphicspath{{./images/}}


\begin{document}
\newcommand{\bfr}[2]{\section{#1} \begin{frame}{#1} #2 \end{frame}}

	\title{Project 2 : EMS internals (?)}
		\author{B Vishal Mathews}

	\begin{frame}
    		\titlepage 
	\end{frame}
	
	\begin{frame}
		\tableofcontents
	\end{frame}

\bfr{Improvements/Additions to previous EMSs}{

    \begin{itemize}
        \item Though Current EMSs have a lot of features, they lack some important features. 
        \item It is heavily Internet depended. Only few offer a download/view online option .For most part downloading and viewing offline is not possible. 
        \item Adding "View offline" option could be a lot advantageous for students.
        \item Unacademy provides practice quizzes but the accuracy again needs to be checked. There is no followup mechanism to challenge the answer key.
    \end{itemize}
        
}
        
\begin{frame}
        \begin{itemize}
        \item Students and Faculty interaction only happens during online classes. Or students ask doubts in a FAQ type of thread available to them.
        \item For the most part no personal doubt clearance is given. 
        \item A way for a student to clear his doubts directly from the faculty can be added.
        \item Most of the EMSs work on batch grouping. Making courses instead of batches creates more flexibility for learning.
        \item A feature for students/parents to see a teachers qualification in teachers' can be added.
        
    \end{itemize}
    
\end{frame}





\end{document}