\documentclass{beamer}

\begin{document}

\begin{frame}{Famous EMIS's in India}

\begin{itemize}
    \item Byju's, Unacademy, Vedantu, Doubtnut, etc. are some of the most popular EMIS's used in India.

    \item All of the above mentioned EMIS's offer vasts amounts of comprehensive study material, ranging from study material for grades I-XII, to that for competitive exams such as JEE, NEET, GATE, etc.

    \item These also track the students' progress through various courses and tests, and provide a detailed analysis for the students to evaluate their strengths and weaknesses. They may also use various representations such as graphs, pie-charts, etc. to provide visual aid in the analysis.

\end{itemize}

\end{frame}

\begin{frame}

\begin{itemize}

\item Byju's also provides interactive videos and tests, which has helped it reach the position of the best EMIS in India.

\item Unacademy offers a variety of offline courses, which the students can complete at their own pace, and, at the same time, have their doubts cleared by teachers.

\item Doubtnut offers a very useful feature :- students can directly scan their question from a camera or an image, and the software automatically finds a solution from the millions of solutions available in their database. It has a very interactive website and mobile app; moreover, it also has a WhatsApp bot that lets students directly upload a photo of a question, and then provides links to solutions.

\end{itemize}

\end{frame}

\begin{frame}

\begin{itemize}

\item To summarise, these popular EMIS's provide the ability to download lots of online resources such as textbooks, solutions, notes, solved question papers, reference books, video lectures, etc..

\item They also provide students with a detailed analysis of their progress through various courses and tests.

\item They also provide a platform/forum where students and teachers can discuss about any topic.

\end{itemize}

\end{frame}

\end{document}